Preprocessing: trimming

### 2022-09-15 analysis/preprosessor/trimming.Rmd
remove ggplot2
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

# packages
if (!require("data.table")) {install.packages("data.table"); require("data.table")}
if (!require("ggplot2")) {install.packages("ggplot2"); require("ggplot2")}
if (!require("ggpubr")) {install.packages("ggpubr"); require("ggpubr")}

>>>>

# packages
if (!require("data.table")) {install.packages("data.table"); require("data.table")}
if (!require("ggpubr")) {install.packages("ggpubr"); require("ggpubr")}
